Interacting with Modal Logics \\ in the Coq Proof Assistant

### 2014-12-12 Papers/InProgress/ModalLogicCoq/ModalCoq.tex
update of draft paper

Nevertheless, general automated reasoning support for modal logics is still
not as well-developed as for classical logics. Deduction tools
for modal logics are often limited to propositional, quantifier-free,
fragments \cite{CoLoSS1,CoLoSS2,ConditionalTableaux,COOL,ModalProvers} or tailored to particular
modal logics and their applications \cite{ToDo:StephanMerz}; 
first-order automated deduction techniques based on tableaux, sequent
calculi and connection calculi have only recently been generalized 
and implemented in a few new provers able to directly cope with
modalities \cite{JensOtten}.

@@

The infrastructure that we have implemented for interactive and
automated reasoning in higher-order modal logics will clearly be
useful also outside philosophy; the range of potential applications is
in fact very wide.

>>>>

Nevertheless, general automated reasoning support for modal logics is still
not as well-developed as for classical logics. Deduction tools
for modal logics are often limited to propositional, quantifier-free,
fragments or tailored to particular
modal logics and their applications \cite{CoLoSS1,CoLoSS2,ConditionalTableaux,COOL,ModalProvers,Coalescing}; 
first-order automated deduction techniques based on tableaux, sequent
calculi and connection calculi have only recently been generalized 
and implemented in a few new provers able to directly cope with
modalities \cite{JensOtten}.

@@

The infrastructure that we have implemented for interactive and
automated reasoning in higher-order modal logics will clearly be
useful also outside philosophy; the range of potential applications is very wide.
